RNAseq-other studies

### 2018-03-15 datasets/RNA-Seq/RNAseq-Applications.Rmd

## Data from Recount
We select uniformly processed RNAseq datasets from the (Recount2)[https://jhubiostatistics.shinyapps.io/recount/] data repository. The data are available in the form of Ranged Summarized Experiments. We select 2 human datasets.

>>>>

## Data from Recount
We select uniformly processed RNAseq datasets from the [Recount2](https://jhubiostatistics.shinyapps.io/recount/) data repository. The data are available in the form of Ranged Summarized Experiments. We select 2 human datasets.
